|

### 2023-01-22 paper_comparison/paper_comparison/paper_comparison.Rmd
Attempt to combine seperate plots into one facetted plot for different j

# Data for shape 1
ori_dat <- poly_model(shape = 1, 
                      x = {
                        raw_x <- rand_uniform(-1, 1);
                        closed_form(~stand_dist(raw_x))
                        }, 
                      sigma = 0.05)$gen(300)

# Plot data for shape 1
pp1 <- VI_MODEL$plot(ori_dat) + 
  ggtitle(quote(He[2]:"U")) + 
  theme_light() +
  xlab("Fitted values") +
  ylab("Residuals") +
  theme(axis.text = element_blank())

# Generate and plot data for shape 2. Reuse x and e.
pp2 <- poly_model(shape = 2, 
                  x = {
                    raw_x <- rand_uniform(-1, 1); 
                    closed_form(~stand_dist(raw_x))
                    }, 
                  sigma = 0.05)$
  gen(300, computed = select(ori_dat, x, e)) %>%
  VI_MODEL$plot() +
  ggtitle(quote(He[3]:"S")) + 
  theme_light() +
  xlab("Fitted values") +
  ylab("Residuals") +
  theme(axis.text = element_blank())

# Generate and plot data for shape 3. Reuse x and e.
pp3 <- poly_model(shape = 3, 
                  x = {
                    raw_x <- rand_uniform(-1, 1); 
                    closed_form(~stand_dist(raw_x))
                    }, 
                  sigma = 0.05)$
  gen(300, computed = select(ori_dat, x, e)) %>%
  VI_MODEL$plot() +
  ggtitle(quote(He[6]:"M")) + 
  theme_light() +
  xlab("Fitted values") +
  ylab("Residuals") +
  theme(axis.text = element_blank())

# Generate and plot data for shape 4. Reuse x and e.
pp4 <- poly_model(shape = 4, 
                  x = {
                    raw_x <- rand_uniform(-1, 1); 
                    closed_form(~stand_dist(raw_x))
                    }, 
                  sigma = 0.05)$
  gen(300, computed = select(ori_dat, x, e)) %>%
  VI_MODEL$plot() +
  ggtitle(quote(He[18]:"Triple-U")) + 
  theme_light() +
  xlab("Fitted values") +
  ylab("Residuals") +
  theme(axis.text = element_blank())

patchwork::wrap_plots(pp1, pp2, pp3, pp4, ncol = 4)
```

>>>>

# Facet label
shape_labels <- c('He[2]:"U"', 'He[3]:"S"', 'He[6]:"M"', 'He[18]:"Triple-U"')

# Data for shape 1
dat_shape_1 <- poly_model(shape = 1, 
                          x = {
                            raw_x <- rand_uniform(-1, 1);
                            closed_form(~stand_dist(raw_x))
                            }, 
                          sigma = 0.05)$gen(300) %>%
  mutate(shape = shape_labels[1])

# Generate data for shape 2, 3 and 4. Reuse x and e.
map_df(2:4, function(shape) {
  poly_model(shape = shape, 
                  x = {
                    raw_x <- rand_uniform(-1, 1); 
                    closed_form(~stand_dist(raw_x))
                    }, 
                  sigma = 0.05)$
  gen(300, computed = select(dat_shape_1, x, e)) %>%
  mutate(shape = shape_labels[shape])
}) %>%

  # Combined with data for shape 1
  bind_rows(dat_shape_1) %>%
  VI_MODEL$plot() +
  facet_wrap(~shape, scales = "free_x", labeller = label_parsed, ncol = 4) +
  theme_light() +
  xlab("Fitted values") +
  ylab("Residuals") +
  theme(axis.text = element_blank())
```
